---
title: "Chicago POI Dashboard"
author: "Zack Larsen"
date: "May 20, 2019"
output: 
  flexdashboard::flex_dashboard:
    social: [ "twitter", "facebook", "menu" ]
    navbar:
      - { title: "About Me", href: "https://zacklarsen.github.io/" }
      - { icon: "fa-github", href: "https://github.com/ZackLarsen", align: right}
      - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/larsenzachary/", align: right}
    source: embed
---

```{r setup, include=FALSE, cache=TRUE}
library(pacman)
library(tidyverse)
p_load(flexdashboard, leaflet, leaflet.extras, dplyr, here, conflicted, data.table, jsonlite, kableExtra, glue, geosphere, DT, networkD3, htmltools, geojsonio, magrittr, treemap, highcharter, viridisLite)
conflict_prefer("filter", "dplyr")

here::here() # "/Users/zacklarsen/Zack_Master/Projects/Dataviz/R/Divvy_Flex"

divvy_stations <- fromJSON("https://feeds.divvybikes.com/stations/stations.json")$stationBeanList

red_light_cameras <- fread("/Users/zacklarsen/Zack_Master/Datasets/Chicago/Red_Light_Camera_Locations.csv")

speed_cameras <- fread("/Users/zacklarsen/Zack_Master/Datasets/Chicago/Speed_Camera_Locations.csv")

cta_stations <- fread("/Users/zacklarsen/Zack_Master/Datasets/Chicago/CTA_L_Stations.csv")

cta_bus_stops <- geojsonio::geojson_read("/Users/zacklarsen/Zack_Master/Datasets/Chicago/CTA_Bus_Stops.geojson", what = "sp")

zip_boundaries <- geojsonio::geojson_read("/Users/zacklarsen/Zack_Master/Datasets/Chicago/Boundaries_ZIP_Codes.geojson", what = "sp")

ward_boundaries <- geojsonio::geojson_read(here("data","Boundaries_Wards.geojson"), what = "sp")

neighborhood_boundaires <- geojsonio::geojson_read("/Users/zacklarsen/Zack_Master/Datasets/Chicago/Boundaries_Neighborhoods.geojson", what = "sp")

# Extract lat, lon from location tuple
strip_parens <- function(x){
  str_remove_all(x, "[()]")
}

cta_stations %<>% 
  select(Location) %>% 
  separate(Location, c("Latitude", "Longitude"), sep = ", ") %>% 
  mutate_at(c("Latitude", "Longitude"), strip_parens) %>% 
  mutate_at(c("Latitude", "Longitude"), as.numeric)




# Extract coordinates from geojson list
cta_bus_stops_list <- geojsonio::geojson_read("/Users/zacklarsen/Zack_Master/Datasets/Chicago/CTA_Bus_Stops.geojson", what = "list")

coords <- vector("list", length(cta_bus_stops_list$features)) 

for(i in 1:length(cta_bus_stops_list$features)){
  y <- cta_bus_stops_list$features[[i]]$properties$point_y
  x <- cta_bus_stops_list$features[[i]]$properties$point_x
  coords[[i]] <- paste(y,x,sep = ",")
}

cta_bus_stops_df <- as.data.frame(do.call(rbind,coords))

cta_bus_stops_df %<>% 
  select(V1) %>% 
  separate(V1, c("Latitude", "Longitude"), sep = ",") %>% 
  mutate_at(c("Latitude", "Longitude"), as.numeric)

```


Landing Page
=========================================

Column 
-------------------------------------


### Crimes, plotted using leaflet. This map can be zoomed in on interactively and the station names will be displayed upon clicking the icon.

```{r, cache=TRUE}

#divvy_stations

#red_light_cameras

#speed_cameras

#cta_stations

#cta_bus_stops

leaflet(divvy_stations) %>%
  # Base groups
  addTiles() %>%
  # Overlay groups
  addCircles(~divvy_stations$longitude, ~divvy_stations$latitude, group = "Divvy Stations") %>%
  addCircles(~red_light_cameras$LONGITUDE, ~red_light_cameras$LATITUDE, group = "Red Light Cameras", color = "red") %>%
  addCircles(~speed_cameras$LONGITUDE, ~speed_cameras$LATITUDE, group = "Speed Cameras", color = "yellow") %>%
  addCircles(~cta_stations$Longitude, ~cta_stations$Latitude, group = "CTA L Stations", color = "blue") %>%
  addCircles(~cta_bus_stops_df$Longitude, ~cta_bus_stops_df$Latitude, group = "CTA Bus Stops", color = "green") %>%
  # Layers control
  addLayersControl(
    overlayGroups = c("Divvy Stations","Red Light Cameras","Speed Cameras","CTA L Stations","CTA Bus Stops"),
    options = layersControlOptions(collapsed = FALSE)
  )

```

***

Click on the selectors to highlight different layers of points of interest.


Column {.tabset}
-------------------------------------

### Data

```{r, cache=TRUE, eval=TRUE}

cta_bus_stops <- geojsonio::geojson_read("/Users/zacklarsen/Zack_Master/Datasets/Chicago/CTA_Bus_Stops.geojson", what = "list")

coords <- vector("list", length(cta_bus_stops$features)) 

for(i in 1:length(cta_bus_stops$features)){
  y <- cta_bus_stops$features[[i]]$properties$point_y
  x <- cta_bus_stops$features[[i]]$properties$point_x
  coords[[i]] <- paste(x,y,sep = ",")
}

cta_bus_stops_df <- as.data.frame(do.call(rbind,coords))

cta_bus_stops_df %<>% 
  select(V1) %>% 
  separate(V1, c("Latitude", "Longitude"), sep = ",") %>% 
  mutate_at(c("Latitude", "Longitude"), as.numeric)

```   


### Crimes Involving Use of Firearm
    
```{r, cache=TRUE, eval=FALSE}

crimes %>% 
  filter(grepl("GUN",Description)) %>% 
  select(`Case Number`, Date, `Primary Type`, Description) %>% 
  arrange(Date) %>% 
  head(n=20) %>% 
  kable() %>% 
  kable_styling()

```


### Arrests Made
    
```{r, cache=TRUE, eval=FALSE}

crimes %>% 
  filter(Arrest == TRUE) %>% 
  select(`Case Number`, Date, Arrest, `Primary Type`, Description) %>% 
  arrange(Date) %>% 
  head(n=20) %>% 
  kable() %>% 
  kable_styling()

```


Statistical {.storyboard}
=========================================

These visualization convey information about distributions and uncertainty.

### Popup

```{r, cache=TRUE, eval=FALSE}

crimes_popup <- crimes %>% 
  mutate(
    popup_text = paste(
      sep = "<br/>",
      glue("<b><a>{`Primary Type`}</a></b>"),
      Description,
      Date,
      paste(Latitude, Longitude, sep=', ')
    )
  ) %>% 
  na.omit()

my_map <- leaflet(crimes_popup) %>%
  addTiles() %>%
  addMarkers(lat = crimes_popup$Latitude,
             lng = crimes_popup$Longitude,
             label = lapply(crimes_popup$popup_text, HTML)
             )
my_map

```


Categorical {.storyboard}
=========================================

These visualizations correspond to count data obtained by aggregating by certain levels or factors and count the number of observations for each category or subcategory.

### Treemap

```{r, cache=TRUE, eval=FALSE}

thm <- 
  hc_theme(
    colors = c("#1a6ecc", "#434348", "#90ed7d"),
    chart = list(
      backgroundColor = "transparent",
      style = list(fontFamily = "Source Sans Pro")
    ),
    xAxis = list(
      gridLineWidth = 1
    )
  )

treemap_data <- crimes %>% 
  select(`Case Number`, `Primary Type`, Description) %>% 
  group_by(`Primary Type`, Description) %>% 
  summarise(Count = n_distinct(`Case Number`))

tm <- treemap(treemap_data, index = c("Primary Type", "Description"),
              vSize = "Count", vColor = "Count",
              type = "value", palette = rev(viridis(6)))

highchart() %>% 
  hc_add_series_treemap(tm, allowDrillToNode = TRUE,
                        layoutAlgorithm = "squarified") %>% 
  hc_add_theme(thm)

```


Geospatial {.storyboard}
=========================================

This board is for displaying information about coordinate points or geospatial features such as countries, states, counties, rivers, elevation, etc.

### Clusters

```{r, cache=TRUE, eval=FALSE}

crimes_full <- crimes %>% na.omit()

leaflet(crimes_full) %>%
  addTiles() %>%
  addMarkers(
    lat = crimes_full$Latitude, 
    lng = crimes_full$Longitude,
    clusterOptions = markerClusterOptions()
  )

```


### Custom Gun Icons

```{r, cache=TRUE, eval=FALSE}

# https://rstudio.github.io/leaflet/markers.html
gunIcon <- makeIcon(
  iconUrl = here("handgun.png"),
  iconWidth = 35, iconHeight = 35,
  iconAnchorX = 0, iconAnchorY = 10
)

leaflet(crimes %>% filter(grepl("GUN",Description)) %>% na.omit()) %>%
  addTiles() %>%
  addMarkers(~Longitude, ~Latitude, icon = gunIcon)

```


### Tile Layers

```{r, cache=TRUE, eval=FALSE}

leaflet(crimes) %>%
  # Base groups
  addTiles(group = "Default") %>%
  addProviderTiles(providers$Stamen.Toner, group = "Toner") %>%
  addProviderTiles(providers$NASAGIBS.ViirsEarthAtNight2012, group = "NASA") %>%
  addProviderTiles(providers$Stamen.Watercolor, group = "Watercolor") %>% 
  # Overlay groups
  addCircles(~Longitude, ~Latitude, group = "Crimes") %>%
  # Layers control
  addLayersControl(
    baseGroups = c("Default", "Toner", "NASA", "Watercolor"),
    overlayGroups = c("Crimes"),
    options = layersControlOptions(collapsed = FALSE)
  )

```


### Custom icon colors

```{r, eval=FALSE}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(crimes)
)

leaflet(crimes) %>%
  addTiles() %>%
  addAwesomeMarkers(~Longitude, ~Latitude, icon=icons, label=~as.character(`Primary Type`))

```


### Heatmap

```{r, cache=TRUE, eval=FALSE}

leaflet(crimes) %>%
  addTiles() %>% 
  addHeatmap(lng=~Longitude,
             lat=~Latitude,
             radius = 8)

```


Ward Features {.storyboard}
=========================================


### Crime Totals By Ward

```{r, cache=TRUE, eval=FALSE}

ward_totals <- crimes %>% 
  select(Ward, `Primary Type`) %>% 
  group_by(Ward) %>% 
  summarise(n()) %<>% 
  mutate(count = `n()`)

ward_totals <- setNames(ward_totals$count, as.character(ward_totals$Ward))

ward_boundaries$crime_total <- ward_totals

labels <- sprintf(
  "<strong>Ward #%s</strong><br/> %g crimes committed in this ward",
  ward_boundaries$ward, ward_boundaries$crime_total
) %>% lapply(htmltools::HTML)


qpal <- colorQuantile("Reds", ward_boundaries$crime_total, n = 10)

leaflet(ward_boundaries) %>%
  addTiles() %>%
  addPolygons(fillColor = ~qpal(crime_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              highlight = highlightOptions(
                weight = 3, # This is the width of the dashed line
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE),
              label = ~labels,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>% 
  addLegend(pal = qpal, 
            values = ~crime_total,
            opacity = 0.7, 
            title = "Crime Count Quantile",
            position = "topright")

```


Custom {.storyboard}
=========================================

This board is for visualizations that might not appear frequently in many examples. Some of them may be easily created by adding a few options to more popular plots, whereas some others require creative thinking and harnessing the power of visualization packages that goes well beyond pre-defined functions.

### Dumbbell (Love) plot

```{r, cache=TRUE, eval=FALSE}

```
